---
title: "Coding project 2: linear models for regression and binary classification."
author: "Nicholas Anderson, Jacob Lemon, Megan Mikami"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
data(spam, package="ElemStatLearn")
data(SAheart, package="ElemStatLearn")
data(zip.train, package="ElemStatLearn")
data(prostate, package="ElemStatLearn")
data(ozone, package="ElemStatLearn")

is.01 <- zip.train[,1] %in% c(0,1)

data.list <- list(
  spam=list(
    features=as.matrix(spam[, 1:57]),
    labels=ifelse(spam$spam=="spam", 1, 0)),
  SAheart=list(
    features=as.matrix(SAheart[,1:9]),
    labels=ifelse(SAheart$SAheart=="SAheart", 1, 0)),
  zip.train=list(
    features=zip.train[is.01, -1],
    labels=as.integer(zip.train[is.01, 1]))
  )

n.folds <- 5
results.list <- list()
mean.loss.list <- list()
```

## Data set 1: spam

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 2: SAheart

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 3: zip.train

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 4: prostate

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 5: ozone

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?