---
title: "Report for Project 3 on Neural Networks"
author: "Nicholas Anderson, Megan Mikami"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(neuralNetworks)

data.name.vec <- c(
  "spam",
  "SAheart",
  "zip.train",
  "prostate",
  "ozone")
data.list <- list()
library(ElemStatLearn)
for(data.name in data.name.vec){
  data(list=data.name, package = "ElemStatLearn")
  data.list[[data.name]] <- get(data.name)
}
str(data.list)
```

## Data set 1: spam

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 2: SAheart

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 3: zip.train

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 4: prostate

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?

## Data set 5: ozone

### Matrix of loss values

print out and/or plot the matrix.

comment on difference in accuracy.

### Train/validation loss plots

plot the two loss functions.

What are the optimal regularization parameters?
